### 2025-01-04 manuscript.tex
Reinforcement learning explanation started.

			\subsubsection{Supervised learning}
			For supervised learning a training set is available. The training set consists of numerous observations with predefined inputs and a corresponding output. The inputs are called predictors (also called features) and the output is referred to as the response. The observations represents individual data instances. \cite{TESL}\\
			As an example lets say we want to predict house prices and we have the following training set:\\
			\begin{table}[H]
			\begin{center}
			\begin{tabular}{|c|c|c||c|}
				\hline
				\textbf{Size ($m^2$)} & \textbf{Number of rooms} & \textbf{Location} & \textbf{Price (€)}\\
				\hline
				250 & 4 & Bratislava & 412000\\
				\hline
				390 & 6 & Komárno & 186000\\
				\hline
				180 & 4 & Košice & 375000\\
				\hline
				\multicolumn{4}{|c|}{\cdots} \\
				\hline
			\end{tabular}
			\end{center}
			\caption{Example training set with arbitrary values}
			\end{table}
			In Table 1.1 each row corresponds to a single house for sale. These houses are the observations and each column (excluding the last column) of the table, which represents the attributes of the houses, is a predictor. The last column is the output or the response.\\

\section{Mégegy alfejezet}

>>>>

			\subsubsection{Supervised learning}
			For supervised learning a training set is available. The training set consists of numerous observations with predefined inputs and a corresponding output. The inputs are called predictors (also called features) and the output is referred to as the response. The observations represents individual data instances. \cite{TESL}\\
			As an example lets say we want to predict house prices and we have the following training set:\\
			\begin{table}[H]
			\begin{center}
			\begin{tabular}{|c|c|c|c||c|}
				\hline
				\textbf{Housing type} & \textbf{Size ($m^2$)} & \textbf{Number of rooms} & \textbf{Location} & \textbf{Price (€)}\\
				\hline
				Single-family home & 250 & 4 & Bratislava & 412000\\
				\hline
				Single-family home & 390 & 6 & Komárno & 186000\\ 
				\hline
				Apartment & 55 & 2 & Trnava & 118900\\
				\hline
				Single-family home & 180 & 4 & Košice & 375000\\
				\hline
				\multicolumn{5}{|c|}{\cdots} \\
				\hline
			\end{tabular}
			\end{center}
			\caption{Example training set with arbitrary values}
			\end{table}
			In Table 1.1 each row corresponds to a single house for sale. These houses are the observations and each column (excluding the last column) of the table, which represents the attributes of the houses, is an input, or a predictor. The last column is the output or the response.\\
			The variables (be that predictor or response) can be described as either quantitative or qualitative. Quantitative variables are numerical values, like the size, number of rooms and price of a house in Table 1.1. Qualitative variables take values in one of $K$ different categories, like the type of housing in Table 1.1. Problems with a quantitative response are referred to as regression problems, while problems with qualitative a response are referred to as classification problems. \cite{AISL}\\
			For each predictor measurement vector $x_i$ (where $i = 1, ..., n$), there is a corresponding response measurement $y_i$. The goal of learning is to fit a model that links the response to the predictors, either to predict the response for future observations or to gain a deeper understanding of the relationship between the response and the predictors. \cite{AISL}\\
			CONTINUE EXPLAINING THE FITTING METHOD USED IN THE FINISHED PROGRAM OR COMMON METHODS\\

			\subsubsection{Unsupervised learning}
			If we only have a set of unlabeled measurement vectors $x_i$ (where $i = 1, ..., n$) with no corresponding $y_i$ response, we talk about unsupervised learning. Since we don't have an associated response, the goal of unsupervised learning is not to make predictions, but rather to analyze and discover patterns in the available data, which often makes working with unsupervised learning algorithms subjective. Furthermore, the lack of a corresponding response makes evaluating the obtained results difficult, as there is no way to check our work without knowing the true answer. This method of learning is often used as part of an exploratory data analysis. For example, a researcher might analyze gene expression levels in patients with certain health conditions to identify relationships or subgroups among the genes. A webstore could perform sales analyses to identify groups of customers with similar purchase histories for targeted advertisements and service customization. Similarly, a search engine might customize search results for users based on the click histories of other users with similar search patterns. \cite{AISL} \\
			For applications like these, where groups of objects or persons are identified, clustering algorithms are used. Another frequently used method in unsupervised learning is data visualization, which transforms complex, unlabeled data into a format suitable for plotting or further analysis. A related task is dimensionality reduction, where the aim is to simplify data with minimal information loss by performing feature extraction and merging correlated features. Anomaly detection algorithms can be used to detect fraudulent actions or to remove outliers from datasets during preprocessing. \cite{HMLSKT}

			\subsubsection{Reinforcement learning}
\section{Mégegy alfejezet}
